Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta-analysis

### 2019-11-05 manuscript/manuscript.Rmd
more work on plot to do
additional study added

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
```

@@

data_core <- data %>% #eshragi overall
  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

@@

data_conflict <- data_core %>% 
  filter(`Funding/equipment/conflict with ZHF company` == "Yes")

@@

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
# https://github.com/awconway/ggprisma
ggprisma::ggprisma(retrieved = 129, included = 15, duplicates = 35, full_text = 21, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
```

>>>>

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
```

@@

#eshragi overall
data_core <- data %>% 
  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

@@

data_conflict <- data_core %>% 
  filter(`Funding/equipment/conflict with ZHF company` == "No")

@@

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
# https://github.com/awconway/ggprisma
ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, full_text = 22, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
```
